additional3D

### 2021-07-13 af2.Rmd
one file df, abm, analysis

setwd("C:/Users/rocpa/OneDrive/Desktop/AF/ethnic-value_multinomial-master/additional/")

@@

valueminority.labs <- c("ß value liberals minority: 0", "ß value liberals minority: 1", "ß value liberals minority: 7")
names(valueminority.labs) <- c("0","1","7")
valuemajority.labs <- c("ß value liberals majority: 0", "ß value liberals majority: 1", "ß value liberals majority: 7")
names(valuemajority.labs) <- c("0","1","7")
ethnicminority.labs <- c("ß ethnic liberals minority: 0", "ß ethnic liberals minority: 1", "ß ethnic liberals minority: 7")
names(ethnicminority.labs) <- c("0","1","7")
ethnicmajority.labs <- c("ß ethnic liberals majority: 0", "ß ethnic liberals majority: 1", "ß ethnic liberals majority: 7")
names(ethnicmajority.labs) <- c("0","1","7")
ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
names(ethnicity.labs) <- c("50","60","70","80","90")

mech <- read.csv("mech_lib.csv",sep=",")
excl <- names(mech) %in% c("run", "density","step")
mech <- mech[!excl] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_3D <- read.csv("3D.csv",sep=",")
excl3D <- names(df_3D) %in% c("run", "density","step")
df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_etlib <- read.csv("df_etlib_all.csv",sep=",")
excl <- names(df_etlib) %in% c("run", "density","step")
df_etlib <- df_etlib[!excl] %>% group_by(ID,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_sec <- read.csv("df_secondary.csv",sep=",")
exclet <- names(df_sec) %in% c("run", "density","step")
df_sec <- df_sec[!exclet] %>% group_by(ID,RND,eth_con_loc,eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

df_3Do <- read.csv("3D_old.csv",sep=",")
excl3D <- names(df_3Do) %in% c("run", "density","step")
df_3Do <- df_3Do[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)

# value_dominant_den <- read.csv("dom_sqr_2.csv",skip = 6,sep = ",")
# leg <- read.csv("leg_value_dominant_den.csv",sep=";")
# 
# value_dominant_den$ID <- "square"
# value_dominant_den2 <- read.csv("dom_crl_2.csv",skip = 6,sep = ",")
# names(value_dominant_den2) <- leg[,1]
# value_dominant_den2$ID <- "circle"
# 
# value_dominant_den <- rbind(value_dominant_den,value_dominant_den2)
# 
# write.csv(value_dominant_den,"value_dominant_den.csv",row.names = F)

value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
excl <- names(value_basic_den) %in% c("run","density","step")
value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)

value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
excl <- names(value_dominant_den) %in% c("run","density","step")
value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean)

dv <- c("step",
"et_sq",
"et_cl",
"vl_sq",
"vl_cl",
"et_sq_bl",
"et_cl_bl",
"et_sq_or",
"et_cl_or",
"vl_sq_bl",
"vl_cl_bl",
"vl_sq_or",
"vl_cl_or",
"den_sq_bl",
"den_sq_or",
"den_cl_bl",
"den_cl_or",
"den_sq",
"den_cl",
"de_sq_bl",
"de_cl_bl",
"de_sq_or",
"de_cl_or",
"dv_sq_bl",
"dv_cl_bl",
"dv_sq_or",
"dv_cl_or")
```

@@

```{r test_val-maj, fig.cap= "Checking effect of value liberal = ethnic liberal majority" echo =  FALSE}

df <- read.csv("mj_val_eth.csv",skip=6,sep=",")
lg <- read.csv("lg_mj_val_eth.csv",sep =";")
names(df) <- lg[,1]

df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

df %>% filter(dominant_square == circle_mj) %>% ggplot(aes(x= circle_mj,y = Segra, color = `segregation`, shape = `orientation`)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
 # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
  xlab("ß value liberals majority = ß ethnic liberals majority") +
  ylab("Outcome") +
  facet_wrap(~  `ethnicity` ) +
  theme_bw()+
  theme(legend.position = "bottom")

@@

# Baseline asymmetric: dominant due to ethnic ration
```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}
# Effect of ethnic asymmetry: all beta dominant equal

@@

# df <- df %>% filter(df$dominant <= 15) 
# df <- df %>% filter(df$fraction_blue==50|df$fraction_blue==60|df$fraction_blue==80)

asym_dom <- asym_dom  %>% filter(fraction_blue == 50 | fraction_blue == 80) %>% gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

ggplot(data = asym_dom, aes(x = dominant, y = Segra, color = `segregation`, linetype = as.factor(fraction_blue))) + geom_point() + geom_line() +
  facet_wrap(~ `type`, nrow = 1) +
  scale_color_manual(values = c("green","purple"),labels =  c("Ethnic","Value"),guide = guide_legend(title = "Segregation \ntype")) +
   scale_linetype_manual(values = c("solid","dashed"),labels =  c("50 %","80 %"),guide = guide_legend(title = "% Majority")) +
  ylab("Spatial Clustering") +
  xlab("ß dominant") +
  theme_bw() +
 theme(legend.position = "bottom")

@@

```{r by-product_cons_original, fig.cap="Effect of liberals majority vs minority on value segregation conservatives", echo = FALSE}
# It goes
# ethnic and value segregation for each group in the annex

##### 
# By-product value of conservatives by value preference liberals

# Majority

mech_cons <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key=ethnics, value=Clust, dv_sq_bl,dv_sq_or)

cons_maj <- ggplot(data = mech_cons, aes(x=val_lib_loc,y=Clust,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_min,dir="v",labeller = labeller(val_lib_min = valueminority.labs)) +
    scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  xlab("ß value liberal majority") + ylab("Spatial clustering") +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
  theme_bw()

# Minority

mech_lib <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key=ethnics, value=Cluste, dv_sq_bl,dv_sq_or)

cons_min <- ggplot(data = mech_lib, aes(x=val_lib_min,y=Cluste,color=  `ethnics`,linetype= as.factor(fraction_blue))) + geom_point(size=1.5, shape = "square") + geom_line() + 
  facet_wrap(~val_lib_loc,dir="v",labeller = labeller(val_lib_loc = valuemajority.labs)) +
  xlab("ß value liberal minority") + ylab("Spatial clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  geom_hline(yintercept=1,color="red") +
  scale_color_manual(values=c("blue","darkorange"),labels=c("Majority","Minority"),name="Ethnicity") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
   guides(color  = guide_legend(order = 1), linetype = guide_legend(order = 2)) +
 theme_bw()

ggplotly(cons_maj)
ggplotly(cons_min)

lib_cons <- ggpubr::ggarrange(cons_maj,cons_min, common.legend = TRUE, legend = "bottom")

# ggsave("lib_cons.jpg",plot=lib_cons)
ggpubr::annotate_figure(lib_cons,
               top = "Effect of liberals majority vs minority on value segregation conservatives")
```

```{r beta_maj, fig.cap="effect liberals one  dataset", echo = FALSE}
# It goes
#####
# Ethnic and value of liberals above each other
mech_vlmj <- mech %>% filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_min==0 | val_lib_min==1 |val_lib_min==7) %>% gather(key = segregation, value = Clustmj, de_cl_bl, dv_cl_bl)

librmj <- ggplot(data=mech_vlmj,aes(x=val_lib_loc,y = Clustmj,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="blue") + geom_line(color="blue") +
facet_wrap(~val_lib_min,dir="v",labeller=labeller(val_lib_min=valueminority.labs)) +
  xlab("ß value liberals majority") + ylab("Spatial Clustering") +
  scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority" ) +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation" ) +
 ggtitle("Liberals Majority") +
    geom_hline(yintercept=1,color="red") +
  guides(color = "black") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mech_vlmn <- mech %>%  filter(fraction_blue == 50 | fraction_blue == 80) %>%  filter(val_lib_loc==0 | val_lib_loc==1 |val_lib_loc==7) %>% gather(key = segregation, value = Clustmn, de_cl_or, dv_cl_or)

librmn <- ggplot(data=mech_vlmn,aes(x=val_lib_min,y = Clustmn,shape=`segregation`,linetype=as.factor(fraction_blue))) + 
  geom_point(size=1.5,color="orange") + geom_line(color="orange") +
facet_wrap(~val_lib_loc,dir="v",labeller=labeller(val_lib_loc=valuemajority.labs)) +
 scale_y_continuous(breaks= seq(0,2,by=0.25)) +
  xlab("ß value liberals minority") + ylab("Spatial Clustering") +
    scale_linetype_manual(values=c("solid","dashed"),labels=c("50%","80%"),name="% Majority") +
  scale_shape_manual(values=c("square","circle"),labels=c("Ethnic","Value"),name="Segregation") +
    geom_hline(yintercept=1,color="red") +
    guides(  linetype = guide_legend(order = 1), shape = guide_legend(order = 2)) +
 #  guides(color=FALSE) + 
    ggtitle("Liberals Minority") +
    geom_hline(yintercept=1,color="red") +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggplotly(librmj)
ggplotly(librmn)

lib_lib <- ggpubr::ggarrange(librmj,librmn, common.legend = TRUE, legend = "bottom")

lib_lib
# ggsave("lib_lib.jpg",plot=lib_lib)

@@

```{r lib_min, fig.cap="Each grouptype, distribution liberals faceted by ethnic ratio", echo = FALSE}

df_fin <- df_3D %>% mutate(RND = case_when(
  val_lib_loc==5 & val_lib_min==5 & eth_con_loc == 5 & eth_con_min == 5 ~ "H",
  val_lib_loc==20 & val_lib_min==20 & eth_con_loc == 20 & eth_con_min == 20 ~ "L"))

sb <- list(
  as.data.frame(cbind((subset(df_fin, eth_lib_loc == 0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority",tt = "cmj")),
           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority",tt = "lmj")),
            as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority",tt = "cmn")),
           as.data.frame(cbind((subset(df_fin, eth_lib_loc  ==  0 & eth_lib_min  ==  0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority",tt = "lmn")),

   as.data.frame(cbind((subset(df_fin, eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_sq_bl,dv_sq_bl)),t="Conservative Majority_et",tt = "cmj_et")),
           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_bl,dv_cl_bl)),t="Liberal Majority_et",tt = "lmj_et")),
            as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0)  %>% gather(subgroup, Segra, de_sq_or,dv_sq_or)),t="Conservative Minority_et",tt = "cmn_et")),
           as.data.frame(cbind((subset(df_fin,  eth_lib_loc != 0 &  eth_lib_min != 0) %>% gather(subgroup, Segra, de_cl_or,dv_cl_or)),t="Liberal Minority_et",tt = "lmn_et"))
           )

for (i in sb) {
pl <-  ggplot(i, aes(x=circle_orange,y=Segra,shape = subgroup, color = RND)) + geom_point() + geom_line() +
  scale_shape_manual(values = c("square","circle"),labels = c("ethnic","Value"), guide = guide_legend(title = "Segregation", order = 1)) + 
    scale_color_manual(values = c("green","purple"),labels = c("high","low"), guide = guide_legend(title = "Randomness")) + 
 scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  xlab("% Liberals Minority") +
  ylab("Spatial Clustering") +
  geom_hline(yintercept=1,color="red") +
  facet_wrap(~ fraction_blue, nrow = 1, labeller = labeller(fraction_blue = ethnicity.labs)) +
 ggtitle(i$t) +
  theme_bw() +
  theme(panel.spacing = unit(0.7, "lines"), legend.position = "bottom")

plot(pl)
nmn <- paste0(as.name(i$tt),".jpg")
ggsave(nmn, pl,  path = "images")
}

@@

```{r combine majority}

sens_vlmj1 <- read.csv("sens_vlmj.csv",skip=6,sep=",")
names(sens_vlmj1) <- read.csv("lg_full.csv",sep=";")[,1]

sens_vlmj2 <- read.csv("sens_vlmj2.csv",skip=6,sep=",")
names(sens_vlmj2) <- read.csv("lg_full.csv",sep=";")[,1]

sens_vlmj <- rbind(sens_vlmj1,sens_vlmj2)
sens_vlmj$ID <- "mj"

sens_vlmn <- read.csv("sens_vlmn.csv",skip = 6, sep= ",")
names(sens_vlmn) <- read.csv("lg_full.csv",sep=";")[,1]
sens_vlmn$ID <- "mn"

sens_vl <- rbind(sens_vlmj,sens_vlmn)

write.csv(sens_vl,"sens_vl.csv",row.names = F)

mj <- sens_vl %>% filter(ID == "mj") %>% filter(type == "Liberals Majority" | type == "Liberals Minority") %>% ggplot(aes(x=val_lib_loc,y=Segra, color = segregation, linetype = as.factor(val_lib_min))) + geom_point() + geom_line() + 
  facet_wrap(~ type)

mj

@@

# Increase ethnic

```{r OK Ethnic preference liberals, fig.cap= "Same preferences ethnic and value, liberals", echo =  FALSE}

df1 <- read.csv("et_mj.csv", skip=6)
df2 <- read.csv("et_mj2.csv", skip=6)
df3 <- read.csv("et_mn.csv", skip=6)
df4 <- read.csv("et_mn2.csv", skip=6)

df <- rbind(df3,df4)
lg <- read.csv("lg_et_mj.csv", sep=";")[,1]

names(df) <- lg

excldf <- names(df) %in% c("run", "density","step")
df <- df[!excldf]

df <- df %>% group_by(fraction_blue,circle_blue,circle_orange,dominant,et_mj_on,et_mn_on) %>% summarise_all(mean)

df <- df %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

df %>% filter(et_mj_on == "false") %>% ggplot(aes(x= dominant,y = Segra, color = `segregation`, shape = `orientation`, linetype = et_mn_on)) + geom_point() + geom_line() +
  scale_color_manual(values = c("green","purple"), guide = guide_legend(title = "Outcome")) +
  scale_shape_manual(values = c("square","circle"), guide = guide_legend(title = "Orientation"))  +
 # scale_y_continuous(limits=c(0.45,1), breaks=seq(0.5,1,by=0.1)) +
  xlab("beta") +
  ylab("Outcome") +
  facet_wrap(~  `type` ) +
  theme_bw()+
  theme(legend.position = "bottom")

@@

@@

@@

We only look at the behavior of liberals, as conservatives have minimal consequence. Combining the two plots looked awful

```{r et_liberals, fig.cap="OK Effect of ethnic liberals majority vs minority on liberals", echo = FALSE}

etlib_maj <- df_sec %>% filter(fraction_blue == 50 | fraction_blue == 80)  %>% gather(key = subgroup, value = Clustetmj, de_cl_bl,dv_cl_bl,de_cl_or,dv_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_cl_bl","de_cl_or"), "Value" = c("dv_cl_bl","dv_cl_or") ),"Ethnic"),
              `ethnicity` = fct_relevel(fct_collapse(subgroup,"Liberals Majority" = c("de_cl_bl","dv_cl_bl"), "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Liberals Majority"))

>>>>

setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/analysis")

@@

# To combine dataframes
# dfg <- function(x,id){
# lg <- read.csv("code_dv.csv", sep = ";")
# x <- rbind(read.csv(paste0(x,".csv"),sep = ",",skip = 6),read.csv(paste0(x,".csv"),sep = ",",skip = 6))
# names(x) <- lg[,1]
# x$ID <- id
# as.data.frame(x)
# }
# 
# bsl <- dfg("bsl_dom_sec","bsl")
# bsl_dom <- dfg("bsl_dom","bsl_dom")
# bsl_sec_cl <- dfg("bsl_dom_sec_circle","bsl_sec_cl")
# bsl_sec_sq <- dfg("bsl_dom_sec_square","bsl_sec_sq")
# sens_lib  <- dfg("sens_lib" ,"sens_lib")
# sens_con  <- dfg( "sens_con" ,"sens_con")
# bsl_lib_con   <- dfg("bsl_value_lib_con","bsl_lib_con")
# bsl_con_lib  <- dfg("bsl_value_con_lib","bsl_con_lib")
# hmp  <- dfg("bsl_dom_sec_htmp","hmp")
# asm  <- dfg("asym_bsl_sec","asm")
# asm_dom  <- dfg("asym_bsl_secno","asm_dom")
# libmj  <- dfg("asym_libmj_mn","libmj")
# libmn  <- dfg("asym_libmn_mj","libmn")
# dislib  <- dfg("asym_dislib","dislib")
# dislib_maj  <- dfg("asym_dislib_libmajL","dislib_maj")
# dislib_min  <- dfg("asym_dislib_libminL","dislib_min")
# etlib_bsl  <- dfg("asym_et_bsl","etlib_bsl")
# etlib_maj  <- dfg("asym_et_mj","etlib_maj")
# etlib_min  <- dfg("asym_et_mn","etlib_min")
# dislibet_maj  <- dfg("asym_dislib_et_mj", "dislibet_maj")
# dislibet_min  <- dfg("asym_dislib_et_mn","dislibet_min")
# 
# df_tot <- rbind(bsl,bsl_dom, bsl_sec_cl, bsl_sec_sq,sens_lib,sens_con,bsl_lib_con ,bsl_con_lib ,hmp,  asm , asm_dom , libmj , libmn  ,dislib , dislib_maj,dislib_min  ,etlib_bsl,etlib_maj ,etlib_min ,dislibet_maj ,dislibet_min)
# 
# 
# write.csv(df_tot,"df_tot.csv",row.names = F)

df <- read.csv("df_tot.csv",sep =",")

# 
# 
# 
# 
# df_3D <- read.csv("3D.csv",sep=",")
# excl3D <- names(df_3D) %in% c("run", "density","step")
# df_3D <- df_3D[!excl3D] %>% group_by(eth_con_loc, eth_con_min,eth_lib_loc,eth_lib_min,val_lib_loc,val_lib_min,val_con_loc,val_con_min,circle_orange,circle_blue,fraction_blue) %>% summarise_all(mean)
# 
# 
# value_basic_den <- read.csv("value_basic_den.csv",sep = ",")
# excl <- names(value_basic_den) %in% c("run","density","step")
# value_basic_den <- value_basic_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,circle,square) %>% summarise_all(mean)
# 
# 
# value_dominant_den <- read.csv("value_dominant_den.csv",sep = ",")
# excl <- names(value_dominant_den) %in% c("run","density","step")
# value_dominant_den <- value_dominant_den[!excl] %>% group_by(ID,fraction_blue,circle_blue,circle_orange,dominant_square,dominant_circle,secondary_square,secondary_circle) %>% summarise_all(mean) 
#

@@

@@

# Baseline asymmetric: dominant due to ethnic ration

```{r asym_baseline, fig.cap="Fig. 8 orig", echo = FALSE}

@@

asym_dom <-  read.csv("df_asym_dom.csv",sep = ",") %>% select(-c(run,density,step)) %>% group_by(dominant,circle_orange,circle_blue,fraction_blue,secondary) %>% summarise_all(mean) %>% 
  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority")) %>%
  filter(fraction_blue == 50 | fraction_blue == 80)

asym_dom <- ggplot(data = asym_dom, aes(x = dominant, y = Segra, color = `segregation`, linetype = as.factor(fraction_blue))) + geom_point(size = 1.5) + geom_line() +
  facet_wrap(~ `type`, nrow = 1, scales= "free") +
  scale_color_manual(values = c("dark green","purple"),labels =  c("Ethnic","Value"),guide = guide_legend(title = "Segregation")) +
   scale_linetype_manual(values = c("solid","dashed"),labels =  c("50 %","80 %"),guide = guide_legend(title = "% Majority")) +
  ylab("Spatial Clustering") +
  xlab("ß dominant") +
    geom_hline(yintercept=1,color="red") +
  theme_bw() +
 theme(legend.position = "bottom")

ggsave("asym_dom.jpg",asym_dom, path = "images", width = 9, height = 4, dpi = 300)

@@

```{r plot asym}

asym.plot <- function(i){
  suppressWarnings(
ggplot(data = i, aes(x= if(i$ID == "mj"){i$val_lib_loc}else{i$val_lib_min}, y=Segra, color = segregation, linetype = as.factor(if (i$ID == "mj"){i$val_lib_min}else{i$val_lib_loc}))) + geom_point(size = 1.5) + geom_line() +
  facet_wrap(~ type, scales = "free") +
  scale_linetype_manual(values = c("solid","dotted","dashed"),labels = c("0","1","15"), guide = guide_legend(title = 
   if (i$ID == "mj"){ "ß liberal minority"}else{ "ß liberal majority"})) +
  scale_color_manual(values = c("dark green","purple"), labels =  c("ethnic","value"), guide = guide_legend(title = "Segregation")) +
  xlab(if (i$ID == "mj"){ "ß liberal majority"}else{ "ß liberal minority"}) +
  ylab("Spatial Clustering") +
  geom_hline(yintercept=1,color="red") +
  theme_bw() +
  theme(legend.position="right")
)
}

@@

```{r asym liberals}

mnlib <- asym.plot( sens_vl %>%  filter( ID == "mn" & type == "Liberals Minority"))
mjlib <- asym.plot(sens_vl %>%  filter( ID == "mj" & type == "Liberals Majority"))

asym_lib <- suppressWarnings( ggpubr::ggarrange(mnlib,mjlib,ncol=1,nrow=2))

ggsave("asym_lib.jpg",asym_lib,path = "images")

@@

```{r asym conservatives}

mncon <- asym.plot( sens_vl %>%  filter( type == "Conservative Majority" | type == "Conservative Minority") %>% filter(ID == "mn"))
mjcon <- asym.plot(sens_vl %>%  filter( type == "Conservative Majority" | type == "Conservative Minority") %>% filter(ID == "mj"))

asym_cons <- suppressWarnings( ggpubr::ggarrange(mncon,mjcon,ncol=1,nrow=2))

ggsave("asym_cons.jpg",asym_cons,path = "images")

@@

```{r asym dislib}

dislib <- read.csv("dislib.csv",sep = ",") %>% select(-c(run)) %>%
  group_by(density,fraction_blue,circle_blue,circle_orange,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,eth_lib_loc,eth_lib_min,val_con_loc,val_con_min,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

ethnicity.labs <- c("50% Majority", "60% Majority","70% Majority","80% Majority","90% Majority")
names(ethnicity.labs) <- c("50","60","70","80","90")

st <- list(
dislib %>% filter(type == "Conservative Majority"),
dislib %>% filter(type == "Conservative Minority"),
dislib %>% filter(type == "Liberals Majority"),
dislib %>% filter(type == "Liberals Minority")

)

suppressWarnings(
for (df in st) {

pl <- ggplot(data = df, aes(x= circle_orange, y=Segra, color = segregation, linetype = as.factor(ID))) + geom_point(size=1.5) + geom_line() +
  facet_wrap(~ fraction_blue, nrow=1, labeller = labeller(fraction_blue = ethnicity.labs)) +
scale_linetype_manual(values = c(bsl = "solid", mj1 = "dashed", mn1 = "dotted"),labels = c("Basine (ß = 15)","ß liberal majority = 1","ß liberal minority = 1"), guide = guide_legend(title = "Dominant \nPreference:")) +
  scale_color_manual(values = c("dark green","purple"), labels =  c("ethnic","value"), guide = guide_legend(title = "Segregation")) +
  xlab("% Liberals Minority") +
  ylab("Spatial Clustering") +
   scale_x_discrete(limits = seq(10,90 ,by = 10)) +
  geom_hline(yintercept=1,color="red") +
  ggtitle(df$type) +
  theme_bw() +
  theme(panel.spacing = unit(0.7, "lines"),legend.position="bottom",legend.text=element_text(size=12))

nmn <- c(if(df$type == "Conservative Majority"){"dislib_cn_mj"}, if(df$type == "Conservative Minority"){"dislib_cn_mn"},if(df$type == "Liberals Majority"){"dislib_lb_mj"},if(df$type == "Liberals Minority"){"dislib_lb_mn"})

ggsave(paste0(nmn,".jpg"), pl,path = "images", width = 10, height = 6, dpi = 300)

)

@@

suppressWarnings(

@@

)

@@

# Increase ethnic: distribution liberals

```{r dislib_et}
